Current and future constraints on primordial magnetic fields

### 2017-02-07 pmf.tex
grammar

Reducing the noise in CMB maps will monotonically improve power spectrum measurements. 
The goal of this section is to quantify the magnitude of that improvement: has the information gain saturated, or will further reductions in noise substantially improve PMF searches. 
Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the 11 or 7-parameter cosmological models. 
For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 
Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a major boon to PMF searches. 
In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered till the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).

@@

Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the beam or  calibration of an experiment must be known. 
We find they do not. 
We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of s Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
We find negligible, sub-percent shifts in the forecasted PMF uncertainties for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
The PMF constraints  for all three power law indices considered are insensitive to the beam and calibration uncertainties.

>>>>

Reducing the noise in CMB maps will monotonically improve power spectrum measurements. 
The goal of this section is to quantify the magnitude of that improvement: has the information gain saturated, or will further reductions in noise substantially improve PMF searches. 
Figure~\ref{fig:sensitivity} shows the uncertainty on \apmf{} as a function of the map noise level for the three PMF templates in either the 11 or 7-parameter cosmological models. 
For this figure, we have fixed the rest of the experimental configuration (i.e.~everything except the polarized noise levels) to the values of the CMB-S4 row in Table~\ref{tab:experiments}. 
Clearly, continuing to improve the sensitivity of CMB experiments to CMB-S4 and beyond will be a major boon to PMF searches. 
In the general, 11-parameter cosmological model, the PMF uncertainty does not plateau in any of the three PMF templates considered until the map noise is at or below $0.3\,\ukarcmin$ (a factor of four lower then the fiducial CMB-S4 configuration).

@@

Finally, we consider if searches for PMFs introduce new requirements on the accuracy to which the beam or  calibration of an experiment must be known. 
We find they do not. 
We parameterize the beam uncertainty as a fractional uncertainty on the FWHM of a Gaussian beam, and calibration uncertainty as an overall power uncertainty. 
We find negligible, sub-percent shifts in the forecasted PMF uncertainties for calibration uncertainties from 0.2 to 5\% and beam FWHM uncertainties from 2 to 12.5\%. 
The PMF constraints  for all three power law indices considered are insensitive to the beam and calibration uncertainties.
